% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

% Formatting -----------------------------------------------------------------

\usepackage{tipa}
\usepackage{soul}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{%
    colorlinks,
    linkcolor={blue!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!50!black},
}
\usepackage{geometry}

\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large%
}

\usepackage{longtable}

\setlength\parindent{0em}

% Typefaces ------------------------------------------------------------------

\RequirePackage{fontspec}
\defaultfontfeatures{Scale = MatchLowercase}
\setmainfont{EB Garamond}
\setsansfont{Libertinus Sans}
\setmonofont{Agave}

% Metadata -------------------------------------------------------------------

\def\name{Timothy Gadanidis}

\hypersetup{%
    colorlinks = true,
    urlcolor = black,
    pdfauthor = {\name},
    pdftitle = {\name: Curriculum Vitae},
    pdfsubject = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\geometry{%
    body={6.5in, 8.5in},
    left=1.0in,
    top=1.25in
}

% Headers --------------------------------------------------------------------

\RequirePackage{fancyhdr}
\fancyhf{}
\pagestyle{fancy}
\fancyfoot[C]{{\thepage}}
\newcommand\headtitle[1]{\fancyhead[L]{\caps{#1}}}

\fancyhead[R]{\caps{Curriculum vitae}}

\fancypagestyle{plain}{%
    \renewcommand{\headrulewidth}{0pt}%
    \fancyhf{}%
    \fancyfoot[C]{}%
}

\headtitle{Timothy Gadanidis}

% Ignore warnings ------------------------------------------------------------

\usepackage{silence}
\ErrorFilter*{pdflatex}{You can't}

\hbadness=3000

% Document -------------------------------------------------------------------

\begin{document}
\thispagestyle{plain}

% Title
\centerline{\Huge \scshape \name}
\vspace{0.2em}
\centerline{\large /ˈtɪməθi ˌgædəˈnidɪs/}
\vspace{0.2em}
\centerline{\footnotesize Last updated: \today}

\medskip\hrule height 1pt

\vspace{0.25in}

% Contact
\begin{tabular}{ll}
    Phone: & (289) 685 4150 \\
    Email: & \href{mailto:timothy.gadanidis@mail.utoronto.ca}%
    {\texttt{timothy.gadanidis@mail.utoronto.ca}} \\
    Website: & \href{http://www.gadanidis.ca}{\texttt{gadanidis.ca}}
\end{tabular}%
\hfill%
\begin{minipage}{0.4\linewidth}
    \raggedright\
    %{1401--66 Isabella Street\\ Toronto, ON, M4Y~1N3}
    {%
        \hfill Dept.\ of Linguistics, University of Toronto\\
        \hfill Sidney Smith Building, 4th Floor\\
        \hfill 100 St.\ George Street\\
        \hfill Toronto, Ontario, M5S~3G3\\
    }
\end{minipage}

\section*{Education}
\begin{longtable}{p{0.12\textwidth}p{0.8\textwidth}}
    2018-- & Ph.D. (Linguistics) --- University of Toronto \\
    2017--2018 & M.A. (Linguistics) --- University of Toronto \\
               & \hspace{1em}\emph{Major research paper}: ``Um, about that, uh, variable''
                 (\emph{uh} and \emph{um} in instant messaging) \\
               & \hspace{1em}\emph{Supervisor}: Derek Denis \\
    2013--2017 & Hon. B.A. (Linguistics), high distinction --- University
    of Toronto \\
\end{longtable}

% todo research interests

\section*{Publications}
\begin{longtable}{p{0.14\textwidth}p{0.78\textwidth}}
    (under review) &\textbf{Gadanidis, Timothy}, Angelika Kiss, Lex Konnelly,
    Katharina Pabst, Lisa Schlegl, Poc\-holo Umbal \& Sali Tagliamonte. A
    theoretically-motivated framework for coding stance: Operationalizing
    insights from semantics and pragmatics. \\
    (under review) &\textbf{Gadanidis, Timothy} and Derek Denis. ``Before the rise
    of \emph{um}.'' In \textit{Discourse Pragmatic Variation and Change: Theory,
    Innovations, Contact}. To be published by Cambridge University Press. \\
    (under review) &Nagy, Naomi, Joyce Woo, and \textbf{Timothy Gadanidis}.
    ``Co-variation in Heritage Cantonese in Toronto.'' \\
    (in prep.) &\textbf{Gadanidis, Timothy}. ``Function, distribution and
    meaning of \emph{uh} and \emph{um} in instant messaging.'' \\
\end{longtable}

\section*{Presentations}

\subsection*{Refereed conferences}

\begin{longtable}{p{0.12\textwidth}p{0.8\textwidth}}
    2019 & Bigelow, Lauren, \textbf{Timothy Gadanidis}, Lisa Schlegl, Pocholo
    Umbal, and Derek Denis. Why are wasteyutes a ting? New Ways of Analyzing
    Variation (NWAV) 48. University of Oregon, October 10--12, 2019. \\
    2019 & Nagy, Naomi, \textbf{Timothy Gadanidis}, and Joyce Woo. Covariation
    in Heritage Cantonese in Toronto. UK Language Variation and Change (UKLVC)
    12. Queen Mary University of London. September 3--5, 2019. \\
    2019 & Tagliamonte, Sali, \textbf{Timothy Gadanidis}, Jean-Fran\k{c}ois
    Juneau, Kinza Mahoon, Andrei Munteanu, Lisa Schlegl and Fiona Wilson.
    Sounding like a `Sounder': Dialect accommodation in Ontario, Canada.
    American Dialect Society (ADS) Annual Meeting. New York City. January 3--6,
    2019. \\
    2018 & \textbf{Gadanidis, Timothy}.  `What’s the \emph{uh} for?': Pragmatic
    specialization of \emph{uh} and \emph{um} in instant messaging.  New Ways of
    Analyzing Variation (NWAV) 47.  New York University (New York City). October
    18--21, 2018. \\
    2018 & \textbf{Gadanidis, Timothy}, Nicole Hildebrand-Edgar, Angelika Kiss,
    Lex Konnelly, Katharina Pabst, Lisa Schlegl, Poc\-holo Umbal \& Sali
    Tagliamonte.  Stance, style, and semantics: Operationalizing insights from
    seman\-tic-pragmatics to account for linguistic variation.  New Ways of
    Analyzing Variation (NWAV) 47. New York University (New York City). October
    18--21, 2018. \\
    2018 & \textbf{Gadanidis, Timothy}.  Um, about that, uh, variable: \emph{Uh}
    and \emph{um} in teen instant messaging.  Discourse-Pragmatic Variation \&
    Change 4. University of Helsinki (Helsinki, Finland). May 28--30th, 2018. \\
    2018 & Denis, Derek \& \textbf{Timothy Gadanidis}.  Before the rise of
    \emph{um}.  Discourse-Pragmatic Variation \& Change 4. University of
    Helsinki (Helsinki, Finland). May 28--30th, 2018. \\
\end{longtable}

\subsection*{Refereed workshops}

\begin{longtable}{p{0.12\textwidth}p{0.8\textwidth}}
    2019 & \textbf{Gadanidis, Timothy}. The social meanings of \emph{um} and
    \emph{uh}. Change \& Variation in Canada (CVC) 11. Memorial University (St.
    John's, Newfoundland and Labrador). June 14--15th, 2019. \\
    2019 & Bigelow, Lauren, \textbf{Timothy Gadanidis}, Lisa Schlegl, Pocholo
    Umbal, and Derek Denis.  [d]at's loud, bro: A report on TH-stopping in
    Multicultural Toronto English.  2nd Annual Buffalo-Toronto Workshop on
    Linguistic Perspectives on Variation Within and Across Languages (Toronto).
    March 16, 2019. \\
    2019 & \textbf{Gadanidis, Timothy}, Naomi Nagy, and Joyce Woo.  Co-variation
    in Heritage Cantonese in Toronto.  2nd Annual Buffalo-Toronto Workshop on
    Linguistic Perspectives on Variation Within and Across Languages (Toronto).
    March 16, 2019. \\
    2018 & \textbf{Gadanidis, Timothy}.  `I'll have to steal that\ldots{}
    \emph{um} borrow it': Investigating \emph{uh} and \emph{um} in the instant
    messages of teens and twentysomethings.  Change \& Variation in Canada (CVC)
    10. University of Manitoba and Université de Saint-Boniface (Winnipeg,
    Manitoba). May 4--5th, 2018. \\
    2018 & \textbf{Gadanidis, Timothy}, Nicole Hildebrand-Edgar, Angelika Kiss,
    Lex Konnelly, Katharina Pabst, Lisa Schlegl, Poc\-holo Umbal \& Sali
    Tagliamonte.  Operationalizing style in variationist analysis: stance-taking
    and English complementizers.  Change \& Variation in Canada (CVC) 10.
    University of Manitoba and Université de Saint-Boniface (Winnipeg,
    Manitoba). May 4--5th, 2018. \\
    2018 & Umbal, Pocholo, Lisa Schlegl, Katharina Pabst, Lex Konnelly, Angelika
    Kiss, Nicole Hildebrand-Edgar, \textbf{Timothy Gadanidis} \& Sali
    Tagliamonte.  `I think ∅ it depends on the context': Stylistic variation in
    the use of the zero complementizer.  Change \& Variation in Canada (CVC) 10.
    University of Manitoba and Université de Saint-Boniface (Winnipeg,
    Manitoba). May 4--5th, 2018. \\
    2017 & \textbf{Gadanidis, Timothy}.  Null subjects in Internet English.  9th
    annual LGCU Welcome Workshop. University of Toronto (Toronto, Ontario).
    October 20th, 2017. \\
\end{longtable}

\section*{Teaching}

\subsection*{Teaching assistantships}

\begin{longtable}{p{0.12\textwidth}p{0.8\textwidth}}
    Fall 2019 & LIN251: \emph{Introduction to Sociolinguistics}. Instructor:
    Dr.~Marisa Brook. University of Toronto. \\
    Spring 2018 & LIN102: \emph{Introduction to Linguistics: Sentence Structure
    and Meaning}. Instructor: Dr.~Susana B\'ejar. University of Toronto. \\
    Fall 2018 & LIN101: \emph{Introduction to Linguistics: Sound Structure}.
    Instructor: Dr.~Marisa Brook. University of Toronto. \\
    Spring 2018 & LIN204: \emph{English Grammar}. Instructor: Phil Howson.
    University of Toronto. \\
    Fall 2017 & LIN200: \emph{Introduction to Language}. Instructor: Dr.~Nathan
    Sanders. University of Toronto. \\
\end{longtable}


\section*{Academic work experience}

\begin{longtable}{p{0.24\textwidth}p{0.70\textwidth}}

    June 2019-- & \textit{Research Assistant} for Yoonjung Kang.
    Develop, implement and run an experiment on the effect of speech rate on
    perception of the Japanese quantity distinction for consonants and vowels,
    including recording and manipulating stimuli using Praat and writing the
    experiment script in jsPsych.
    \\

    May 2019-- & \textit{Statistical consulting with R}.
    Paid consultation with colleagues on statistics in R, helping to interpret
    results, create visualizations, and solve programming problems.
    Also done \emph{pro bono}.
    \\

    Sept.\ 2018-- & \textit{Lab Manager and Research Assistant} for Naomi
    Nagy's Heritage Language Variation and Change (HLVC) project.
    Analyse and interpret sociolinguistic data,
    manage payroll for research assistants,
    and various other administrative and research tasks.
    \\

    May 2019 & \textit{Project Manager} for Derek Denis's 2019 Jackman
    Scholars in Residence project.
    Assist undergraduate scholars-in-residence working on Multicultural
    Toronto English by implementing a sociolinguistic survey.
    \\

    Sept.\ 2017 -- May 2018 & \textit{Research Assistant} for Derek Denis.
    Extract, code and visualize sociolinguistic data.
    \\

    March 2017 -- March 2018 & \textit{Research Assistant} for Sali Tagliamonte.
    Visualize sociolinguistic variables based on various social predictors; code
    extracted data based on various predictors for later analysis.
    \\

    May 2014 -- April 2015 & \textit{Lab Assistant} (work-study) for Sali
    Tagliamonte.
    Transcribe sociolinguistic interviews while highlighting
    interesting syntactic features.
    \\

\end{longtable}

\section*{Research grants}
\begin{longtable}{p{0.12\textwidth}p{0.80\textwidth}}
    2019--2022 & Joseph-Armand Bombardier Canada Graduate Scholarship
    (Doctoral), Social Sciences and Humanities Research Council of Canada.
    \$105,000. \\
    2019--2022 & Ontario Graduate Scholarship (Doctoral), University of Toronto
    School of Graduate Studies.
    \$15,000. (declined) \\
\end{longtable}


\section*{Awards and honours}
\begin{longtable}{p{0.12\textwidth}p{0.80\textwidth}}
    2019 & SSHRC Institutional Grant. Funding for recruiting participants for an
    experiment on \emph{uh} and \emph{um} in speech. \$200. \\
    2018 & SSHRC Institutional Grant. Funding for recruiting participants for an
    experiment on \emph{uh} and \emph{um} in IM. \$200. \\
    2018 & Travel Grant from CRC in Language Variation \& Change.  Funding for
    travel to CVC 10, Winnipeg. \$100. \\
    2018 & School of Graduate Studies Conference Grant. Funding for travel to
    DiPVaC 4, Helsinki. \$640. \\
    2018 & SSHRC Institutional Grant. Funding for travel to DiPVaC 4, Helsinki.
    \$250. \\
    2013--2017 & Dean's List, University of Toronto. \\
    2015 & St.\ Michael's College In-course Scholarship. \$1,500. \\
    2013 & University of Toronto Scholarship. \$5,000. \\
\end{longtable}

\section*{Service}
\begin{longtable}{p{0.12\textwidth}p{0.80\textwidth}}
    2019   & Volunteer, Science Rendezvous (outreach day for elementary school
    students). \\
    2018-- & Co-coordinator, Language Variation \& Change Research Group. \\
    2018-- & Reviewer, \textit{Toronto Working Papers in Linguistics}. \\
    2018-- & Coordinator, weekly LGCU (Linguistics Graduate Course Union) pub
    night. \\
    2018-- & Organizing committee member, annual LGCU Welcome Workshop. \\
    2018-- & Informal consulting on statistics with LGCU members. \\
    2017-- & Editor, LGCU Writing Support Committee. \\
    2017-- & Linguistics Department Steward, CUPE 3902, Unit 1 (TA/CI labour
    union). \\
\end{longtable}

\section*{Skills}
\begin{longtable}{p{0.13\textwidth}p{0.80\textwidth}}
    Software &Linux, ELAN, R, PsychoPy, \LaTeX{}, Pandoc, jsPsych, Vim \\
    Languages &English (first language), French (intermediate), Japanese (intermediate),
    Mandarin (beginner)
    \\
    Programming & Rscript, Praat scripting, Python, Haskell, VimL \\
\end{longtable}

\vfill


% Footer

\end{document}
